SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-10-12 doc/manuscript.Rmd
release

---
title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
output: github_document
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

@@

@@

```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database. Each golden circle is a record. The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.*", fig.width=7, fig.height=3}
knitr::include_graphics("../results/Fig1.png")
```

@@

```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app. Records for one species, the European common beech, Fagus sylvatica. Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel. Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.*", fig.width=7, fig.height=5}
knitr::include_graphics("../results/Fig2.png")
```

>>>>

---
title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
output: pdf_document
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

@@

*This is the peer reviewed version of the following article: Fernández-Pascual, E. (2020). SylvanSeeds, a seed germination database for temperate deciduous forests. Journal of Vegetation Science, which has been published in final form at https://doi.org/10.1111/jvs.12960.*

@@

```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Geographical distribution of the germination records in the database. Each golden circle is a record. The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the WWF.", fig.width=7, fig.height=3}
p1
```

@@

```{r fig2, echo = FALSE, fig.cap = "Example of the germination records as shown by the SylvanSeeds app. Records for one species, the European common beech, Fagus sylvatica. Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel. Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.", fig.width=7, fig.height=5}
p2
```
